Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-11-08 Paper/model.tex
Cleaned up the model.pdf to make it look more like a paper.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
{\tt\small dhiman@umich.edu}
Manmohan Chandraker\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  TODO: Write abstract
\end{abstract}

\section{Introduction}
  NEC has already developed a monocular camera based structure from motion
  system which is accurate for requirements of road scene understanding. So we
  assume that egomotion is given as an observed variable in our graphical
  model. And we have following features to our disposal for estimating the 3D
  poses (position + orientation) of traffic participants:
  \begin{description}
    \item[Ground plane] We assume that all the traffic participants lie on a common ground
      plane. This is not particularly true for the cars that are parked off the
      road. However, for autonomous driver assistance applications we can
      ignore those cars.
    \item[Detections] We assume that 2D car detections are available with tracking informations.
    \item[Point tracks] We assume that 2D point tracks are available.
    \item[GPS and Map information] We assume that GPS information is available
      and we use openstreetmaps.org for pulling out local map for the current
      car's position.
    \item[Lane Information] We assume the lane detection works well and lane
      information is available.
    \item[Size prior] The distribution of size of cars follows gaussian distribution.
    \item[Collision] A reasonable output of the system donot has any overlapping cars.
  \end{description}

\section{Notation}
% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

@@

% projection function
\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}(#1)}
\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}

@@

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}

@@

The objective is to find the most likely traffic participant state given various
evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.}, \text{map},
\text{GPS}\}$.

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
  \caption{Graphical model. The six numbered black circles represent the
    unknown state variables of each car. All other nodes in the graphical model
    are assumed
    observed variables. Consider each energy in the model one by one. (1)
    Bounding box energy: The bounding box energy without occlusion modeling is
    a unary term, but with occlusion it becomes a higher order term that
    affects the state of occluder as well. In this graphical model we assume
    that the scene is being observed from left to right, hence "2" occludes "6"
    and "5" and "5" occludes "1". The bounding box detection is represented by
  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
  included in modeling point tracks energy we have similar interdependencies
  for point tracks energy. The available point tracks are modeled by
  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
  mathematically is a dense graph between all the TP but here we represent
  collision among only those TP that are near enough to have a significant
collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
  \label{fig:graphmodel}
\end{figure}

@@

Bhattacharya coefficient $\int_a^b\sqrt{p(x)q(x)}dx$ is a measure of similarity of two
distributions $p(x)$ and $q(x)$. If we represent traffic participants as
gaussians in BEV, then similarity is a measure of collision. Exactly
overlapping distribution results in coefficient as 1. The analytical form of
Bhattacharya coefficient has been taken from
\url{http://like.silk.to/studymemo/PropertiesOfMultivariateGaussianFunction.pdf}

\begin{align}
  \label{eq:collisionEnergyHellingerDistance}
  \EnergyCol &=
  \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
  {|P|^\frac{1}{2}}
  e^{-\frac{1}{8}
    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
    P^{-1}
    \left(\pos{i}{t} - \pos{j}{t}\right)
    }
\end{align}
where 
\begin{align}
  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l^i & 0 \\ 0 & 2/w^i \end{bmatrix}
R_{\ori{i}{t}}
\end{align}

\begin{comment}
  \subsection{Bounding box energy}
  \label{sec:totalBBoxEnergy}
  With abuse of notation we represent the four sides of hypothesized bounding
  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
  bounding box energy becomes a pairwise term.

  \begin{multline}
    \pEnergy{occ}(\relp{i}{t}, \dimsn{i}, \relp{j}{t}, \dimsn{j}) = \\
    \sum_s \rho^{ijs}(t)\projectionOf{\dimsn{i}}_s - \bb{i}_s
               %\sum_{i=1}^N \sum_{t=s_i}^{e_i}
    %\sum_kp_{ik}^{\text{track}}(\projectionOf{\dimsn{i}} - \bb{k})^\top \pmb{\rho}(i,j,t)
  \end{multline}
  where $\rho^{ijs}(t)$ is the visibility fraction of the side $s$ of the
  bounding box. We need to compute visibility fraction we need to compute the
  occlusion mask which is explained in next few sections.

  \subsubsection{Visible faces from bounding boxes}

  \begin{figure}[h]
    \includegraphics[width=\columnwidth]{graphics/maxFacesVisible.pdf}
    \caption{Only three faces can be visible out of six faces of a bounding
    box.}
  \end{figure}

  \newcommand{\minx}{x_{\text{min}}}
  \newcommand{\miny}{y_{\text{min}}}
  \newcommand{\maxx}{x_{\text{max}}}
  \newcommand{\maxy}{y_{\text{max}}}
  \newcommand{\frontface}{F^i_\text{FF}(t)}
  Each bounding box has 6 faces of which only 3 can be visible.
  Sort the vertices in increasing order of depth. The closest vertex has three
  neighboring faces. All the faces that are visible must be a subset of these
  three. Use first three vertices to
  define the front face (say $\frontface$). Also identify the four 3D points
  that correspond to min/max in x and y direction in the image. If all min-max 4
  points are same as vertices of $\frontface$, then we have only one plane
  visible. If $\{\minx, \maxx\} \not\subset \frontface \land \{\miny, \maxy\}
  \not\subset \frontface$ then we have 3 planes visible. Otherwise we have just
  two planes visible. Let number of planes visible be $n_F$.

  \begin{align}
    n_F &= \begin{cases}
    1 & \text{if }\{\minx, \maxx, \miny, \maxy\} =
    \frontface\\
    2 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \subset \frontface \lor
    \{y_{\text{min}}, y_{\text{max}}\} \subset \frontface
    \\
    3 & \text{else if }\{x_{\text{min}}, x_{\text{max}}\} \not\subset \frontface \land
    \{y_{\text{min}}, y_{\text{max}}\} \not\subset \frontface
    \end{cases}
    \label{eq:nfaces}
  \end{align}

  First vertex restrict possible visible faces to three faces. If $n_F = 3$,
  then all three of these faces are visible. If $n_F = 2$, use second closest
  vertex to restrict visible faces to just two. If $n_F = 3$, then front face 
  $\frontface$ is the only visible face.
\end{comment}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}
\begin{comment}
  \subsubsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

  % Sort all planes in increasing order of depth.  This yields a cumulative
  % occlusion mask function
  Occlusion mask is a function that takes the relative depth $d$ from the car
  camera and returns a binary mask that represents occlusions untill that depth.
  Near to the camera occlusion mask is all empty (all zeros) and more occlusions
  get added to the mask with distance.

  \begin{align}
    \occ{d} &= \begin{cases}
    \phi & \text{if } 0 < d \le \relpz{1}{t}\\
    \cup_{i=1}^j \projectionOf{F^i} & \text{if } \relpz{1}{t} < d \le \relpz{j+1}{t}
    \end{cases}
    \label{eq:occlusionmask}
  \end{align}

  where $\relpz{j}{t}$ is the depth of the $j$th traffic participant when sorted
  by increasing depth.

  \subsubsection{Algorithm to get faces based occlusion mask}
  \label{sec:occlusionMaskFromOptVector}

  This is an algorithm to compute occlusion mask Eq.\eqref{eq:occlusionmask}. We
  represent the occlusion mask as a set of polygons.

  Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  \begin{enumerate}
    \item Collect visible faces using Eq.\eqref{eq:nfaces} for all cars
    %\item for each face get its closest and farthest vertex to the camera.
    \item Create a sorted list of faces
    % \item Create a sorted binary tree of
    %   faces indexed by closed vertices.
    \item Loop over list of sorted visible faces
      \begin{enumerate}
        \item Get the face(s) $\{\face\}$ closer to camera than this face
        \item Add the faces to mask polygon (if not already added): \\
          $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\face}$
        \item $d = \relpz{i}{t}$
      \end{enumerate}
  \end{enumerate}

  To get the occlusion mask for a face use the farthest vertex of the face to
  query $\occ{.}$.

  \subsubsection{Visibility fraction of a side}
  Let the center of the projected hypothesized bounding box be $\centerProj$ and
  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
  of the bounding box form a triangle, for example $\triangleProj{1,2} =
  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
  fraction of side is given by
  \begin{align}
    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
                         {\|\triangleProj{s}\|}
     \label{eq:bboxEnergyFromOccMask}
  \end{align}
\end{comment}

\begin{comment}
  \subsection{Occlusion free projection}
  Occlusion free projection can be obtained by applying the precomputed occlusion
  mask to the face projection.
  \begin{align}
    \occFreeProj{\face} &= \projectionOf{\face} \setminus
    \occ{\relpz{i}{t}}
  \end{align}

  \subsection{Perspective-visibility fraction}

  Apart from occlusion, we want to account for the perspective affects. When an 
  objects perspective projection is too small, detection and all related
  evidences deteriorate. One way of this is to find out the projection ratio. In
  fact, we can consolidate projection ratio and occlusion ratio in one term if
  we consider the projection of 3D bounding box planes instead of the entire
  bounding box.

  \begin{align}
    \rho^i_t &= \sum_{k=1}^{n_F}\frac{\relpz{i}{t}^2\|\occFreeProj{F^i_k(t)}\|}{f^2\|F^i_k(t)\|}
  \end{align}

  where $\occFreeProj{.}$ again means occlusion free projection. $f$ is the
  focal length of the camera so that $\frac{f^2}{\relpz{i}{t}^2}\|F^i_k(t)\|$ is
  the area of projected plane if there were no perspective effects.
\end{comment}

\subsection{Continous Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We want continuous modeling of occlusion. We model occlusion as a opacity
term. Based on the dimensions $\dimsn{i}$, we can
compute the covariance matrix $\Sigma_i$ as shown in Sec. 
\ref{sec:sigmacomputation}

So far we have modeled our point tracks energy in a non-smooth way:
\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t-1}}(#1)}
\begin{multline}
  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty a_j^i(\lambda)\|\trackpj{t} - \projectionOf{\invProjectionOf{\trackpj{t-1}}}\|^2 d\lambda
\end{multline}

The tricky part here is inverse projection $\invProjectionOf{.}$ . When we
project an image point back to 3D we get a ray $\lambda K^{-1}\trackpj{t-1}$
which is ambiguous up to a scale factor $\lambda$. Using our hypothesized 3D
layout of the scene we can estimate this scale factor, we
can compute a distribution over the $\lambda$. 
\subsubsection{Occupancy function}
Assuming occupancy to be a
probability distribution over 3D space. For each traffic participant the
occupancy is modeled as a logistic function 
\newcommand{\occf}{f^i_{occ}(\mathbf{x})}
\begin{align}
   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
\end{align}
where $L(.)$ is the logistic function defined by
\begin{align}
  L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
    }
\end{align}
where $d(\mathbf{x},\pos{i}{t-1}) =
(\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
0.9$

We model the probability of a point being projected to a camera is dependent
up two factors, (1) reflection and (2) transmission through intermediate
space. 
\subsubsection{Reflection probability}
For lambertian reflection we replace the surface normal with the
gradient of occupancy.
\begin{align}
  P_{\text{reflection}} = \sum_i (\max \{0, \nabla \occf^\top
  \hat{\mathbf{r}_j}\})^2
\end{align}
where $\hat{\mathbf{r}_j} =
\frac{K^{-1}\trackpj{t-1}}{\|K^{-1}\trackpj{t-1}\|}$ is unit vector in the
direction of ray. The gradient in the direction opposite to ray yields -ve
probability which needs to be clipped off. Squaring the function keep it
smooth near zero.

\subsubsection{Transmission probability}
A model for transmission of light through a material of thickness $x$,
density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
\begin{align}
  I(x) = I_0e^{-k_o\rho x}
\end{align}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

@@

% projection function
\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}

@@

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
\newcommand{\minx}{x_{\text{min}}}
\newcommand{\miny}{y_{\text{min}}}
\newcommand{\maxx}{x_{\text{max}}}
\newcommand{\maxy}{y_{\text{max}}}
\newcommand{\frontface}{F^i_\text{FF}(t)}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}

\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
\newcommand{\occft}[1]{f_{occ}(#1)}

\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}
\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}

\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{(ij)}(\lambda)}
\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
\newcommand{\dishort}{d_i(\mathbf{x})}

\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}

\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}_j}

\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}

\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}

\newcommand{\muit}{\mu^(i)_t}
\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}

\newcommand{\muic}{{\mu^(i)_c}}
\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}

\newcommand{\muiu}{\mu^{(i)}_t}
\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}

\newcommand{\xt}{\mathbf{x}_t}
\newcommand{\xc}{\mathbf{x}_c}

\newcommand{\Rctot}{R}
\newcommand{\tctot}{t}

\newcommand{\tcmut}{t'}

\newcommand{\Beizer}{B\'eizer }

\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small dhiman@umich.edu}
\and
Manmohan Chandraker\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  TODO: Write abstract
  \vspace{4cm}
\end{abstract}

\section{Introduction}

\begin{itemize}
  \item Introduce the problem
  \item Describe our approach
  \item Contrast with Milan's work
  \item Contrast with Andreas Geiger's work
  \item Highlight the contributions
\end{itemize}
\vspace{10cm}
\begin{figure}[t]
  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
  \caption{Graphical model. The six numbered black circles represent the
    unknown state variables of each car. All other nodes in the graphical model
    are assumed
    observed variables. Consider each energy in the model one by one. (1)
    Bounding box energy: The bounding box energy without occlusion modeling is
    a unary term, but with occlusion it becomes a higher order term that
    affects the state of occluder as well. In this graphical model we assume
    that the scene is being observed from left to right, hence "2" occludes "6"
    and "5" and "5" occludes "1". The bounding box detection is represented by
  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
  included in modeling point tracks energy we have similar interdependencies
  for point tracks energy. The available point tracks are modeled by
  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
  mathematically is a dense graph between all the TP but here we represent
  collision among only those TP that are near enough to have a significant
collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
  \label{fig:graphmodel}
\end{figure}

\section{Related Work}
TODO:
\vfill
\pagebreak
Related work continued
\vspace{15cm}

\section{Problem Definition}
TODO:
\vspace{4cm}

\section{Notation}

@@

The objective is to find the most likely traffic participant (TP) state given
various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
\text{map}, \text{GPS}\}$.

@@

@@

\section{Modeling traffic participants}
\label{sec:TPmodel}
Following standard model of occupancy in 3D reconstruction community, we model
the TP's as high occupancy regions in space. We model the
uncertainty in occupancy equivalent of transparency i.e. the regions that are
more certain to be occupied are viewed as relatively more opaque then other
regions. Based on this intuition we model TP's translucent
ellipsoids whose opacity is maximum at the center and drops off away from the
center. More specifically we model, the occupancy of a TP as a
logistic function,

\begin{align}
   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
\end{align}
where $L(.)$ is the logistic function defined by
\begin{align}
  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
    }
\end{align}
where $d(\mathbf{x},\pos{i}{t}) =
(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
dimensions of the TP. Please refer to supplementary material 
for computation of $\Sigma_i$ from TP's dimensions.

We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
(1) reflection and (2) transmission through intermediate space. The reflection
part ensures that there is an object to reflect a point at a certain region in
the 3D space while transmission part models occlusion.
\begin{align}
  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reflection probability}
For Lambertian reflection we replace the surface normal with the
gradient of occupancy.
%
\begin{align}
  \Prefl = (\max \{0, \nabla \occf^\top
  \hat{\mathbf{r}_j}\})^2
\end{align}
%
where $\ray =
\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
direction of ray. The gradient in the direction opposite to ray yields -ve
probability which needs to be clipped off. Squaring the function keep it
smooth near zero.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Transmission probability}
A model for transmission of light through a material of thickness $x$,
density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
%
\begin{align}
  I(x) = I_0e^{-k_o\rho x}
\end{align}
%

Since both opacity and density are represented by the occupancy function
$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
function $1 - \occftot$. So the transmission probability over a small distance
$d\lambda$ is given by
%
\begin{align}
  P_{\text{transmission}}(\lambda + d\lambda) =
  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
\end{align}
%

For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by

\begin{align}
  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
  \Ptrans &=
  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
  \label{eq:ptrans-integral}
\end{align}
where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
$\lambda$.

In practice, the integral for transmission probability
\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
choose a product of sigmoid function that approximates the behaviour of
transmission probability,
%
\begin{align}
\label{eq:evalCumulativePtrans}
  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
\end{align}
%
where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
representing the elliptical projection of $i^{th}$ TP.
$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
depth of the $i^{th}$ TP.
%
\begin{align}
  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
    \muiu))}
  }
  \\
  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
    1 + e^{-k_d(\lambda - \mu^i_d)}
}
\end{align}
%

\begin{comment}%% Comment
  A product integral is a simple integral in log domain
  \begin{align}
    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
  \end{align}
\end{comment}%% Comment

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We explain energies in this section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

\begin{multline}
  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
and $\Ereproj(\lambda)$ is the re-projection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
inverse projection functions that project 3D point to camera image and vice
versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.

\begin{comment}
  \subsubsection{Occupancy function}
  Assuming occupancy to be a
  probability distribution over 3D space. For each TP the
  occupancy is modeled as a logistic function 
  \begin{align}
     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
  \end{align}
  where $L(.)$ is the logistic function defined by
  \begin{align}
    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
      }
  \end{align}
  where $d(\mathbf{x},\pos{i}{t-1}) =
  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
  0.9$
  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
  % $\lambda$. Let
\end{comment}

\begin{comment}
  \subsubsection{Approximations}
  Reflection probability of $i$th TP is easy to compute
  analytically 
  \begin{multline}
    \Prefl =
    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
    \label{eq:analytic-prefl}
  \end{multline}
  where 
  \begin{multline}
    \nabla \occfxi^\top\ray \\=
    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
  \end{multline}
  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
